### 2019-06-28 report/MSc_Report.tex
update

\usepackage{alltt}
\input{header.sty}   % packages, layout and standard macros

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:56 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
Study & Comparison & Outcome & Events & Total & Events\_c & Total\_c \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two results as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Study & Comparison & Outcome \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
\label{barbiturates}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Missing mean values and mean differences & 984 \\ 
  Missing standard deviations and standard errors & 1300 \\ 
  Missing sample sizes & 12173 \\ 
  Missing study year & 44649 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset} 
\label{missing}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Outcome measure & n & Percentage \\ 
  \hline
Risk Ratio & 232583 & 50.1\% \\ 
  Mean Difference & 102315 & 22.1\% \\ 
  Odds Ratio & 49372 & 10.6\% \\ 
  Std. Mean Difference & 40535 & 8.7\% \\ 
  Peto Odds Ratio & 19122 & 4.1\% \\ 
  Hazard Ratio & 6566 & 1.4\% \\ 
  Risk Difference & 6234 & 1.3\% \\ 
  Rate Ratio & 2283 & 0.5\% \\ 
  other & 4810 & 1\% \\ 
   \hline
\end{tabular}
\endgroup
\caption{Frequencies of outcome measures among results. n denotes the total number 
             of results with the outcome measure and percentage the percentage of the outcome measure,} 
\label{outcome.measure.frequencies}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
n & Number of groups & Cumulative sum of groups \\ 
  \hline
1 & 102344 & 186300 \\ 
  2 & 31686 & 83956 \\ 
  3 & 16072 & 52270 \\ 
  4 & 9628 & 36198 \\ 
  5 & 6444 & 26570 \\ 
  6 & 4230 & 20126 \\ 
  7 & 2961 & 15896 \\ 
  8 & 2114 & 12935 \\ 
  9 & 1592 & 10821 \\ 
  10 & 1238 & 9229 \\ 
  11 & 921 & 7991 \\ 
  12 & 702 & 7070 \\ 
  13 & 585 & 6368 \\ 
  14 & 455 & 5783 \\ 
  15 & 5328 & 5328 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Cumulative number of groups with number of reproduction trials >= n} 
\label{repr.groups}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:14:57 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{ccc}
  \hline
Count & Binary Outcomes & Continuous and Survival \\ 
  \hline
  0 & 65.9 \% & 68.4 \% \\ 
    1 & 16.4 \% & 9.6 \% \\ 
    2 & 8.6 \% & 9.1 \% \\ 
    3 & 5.6 \% & 10.6 \% \\ 
    4 & 2.9 \% & 2.3 \% \\ 
    5 & 0.6 \% & NA \% \\ 
   \hline
\end{tabular}
\endgroup
\caption{Counts Number of significant test results per meta-analysis, separated
       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
       applied} 
\label{number.sig.tests}
\end{table}

When only looking at small study effect tests, 29.1\% of binary outcome tests and 26.5\% of survival and continuous outcome tests had at least one significant result. After applying the bonferroni correction for multiple testing, this shrinks to 10.9\& for binary and 12.1\% for continuous and survival outcomes. \\
When comparing significant findings for small study effect tests and excess significance tests, we will only do so with Harbord's or Egger's test. 22.4\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 28\% for continuous and survival outcomes. Again, the numbers change to 13.3\% for binary outcomes and 17.2\% for continuous and survival outcomes after applying the bonferroni correction. \\
3\% have significant Harbord's test result and significant excesss significance test result  (1.1\% with bonferroni). Of the continuous outcomes, we have 6.1 \% with Egger's test and 1.8 with Bonferroni correction.

@@

If one is interested in the mere change in effect size and if the effect size did decrease or increase after adjustment, one can look at Figure \ref{fig:adjustment.size}. It displays the difference between the meta-analysis pooled treatment effect and the adjusted treatment effect. To compare the overall effect of adjustment for small study effects, the absolute value of the effect size is used. Thus, a negative difference indicates larger adjusted treatment effect size than meta-analysis pooled effect size. For better illustration, some very large and very small differences have been ommitted in the $z$-score and Hedges $g$ histogramms; the missing differences are provided in Table \ref{missing.differences}. Additionally to the histogramms, Table \ref{adjustment.difference} shows the quantiles and means for the various differences.
%For sake of interpretability, negative effect sizes are changed to positive, such that a negative difference always means that the adjusted treatment effect is larger than the meta-analysis effect. Vice versa, a positive difference will indicate smaller adjusted effects. \\

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:12:39 2019
\begin{table}[ht]
\centering
\begingroup\tiny
\begin{tabular}{lcccrrrrrrrr}
  \hline
meta.id & file.nr & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
  \hline
2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.43 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
  18658 & 18658 & 2 & 0 & 1.16 & 1.14 & 1.16 & 1.17 & 1.40 & 2.85 & 1.40 & 1.74 \\ 
  46472 & 46472 & 1 & 1 & 1.79 & 1.44 & 1.79 & 0.66 & 0.12 & 6.97 & 6.97 & 0.79 \\ 
  52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
  60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.58 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
  73769 & 73769 & 3 & 1 & -0.14 & 0.00 & 214760.42 & -0.04 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
  79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
  90138 & 90138 & 3 & 0 & 0.31 & 0.80 & 0.31 & 0.55 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
  97356 & 97356 & 2 & 0 & -0.08 & -0.33 & -0.08 & -0.17 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
  98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.91 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 71.80 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
  119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.11 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 498188.34 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects
             of Figure 
ef{fig:adjustment.size}. Abbreviations are used for z-score (z) and Hedges g (g)} 
\label{missing.differences}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Thu Jun 27 15:12:39 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lcccccc}
  \hline
 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
  \hline
z-score: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.05 & 402.37 \\ 
  z-score: Random - Copas & -0.04 & 0.00 & 0.00 & 0.00 & 0.01 & 159.98 \\ 
  z-score: Fixed - Regression & -0.15 & -0.05 & -0.01 & 0.04 & 0.13 & -0.01 \\ 
  z-score: Random - Regression & -0.18 & -0.07 & -0.02 & 0.03 & 0.16 & -0.02 \\ 
  Hedges g: Fixed - Copas & -0.09 & -0.01 & 0.00 & 0.01 & 0.05 & -0.02 \\ 
  Hedges g: Random - Copas & -0.14 & 0.00 & 0.00 & 0.00 & 0.00 & -0.04 \\ 
  Hedges g: Fixed - Regression & -0.39 & -0.13 & -0.04 & 0.04 & 0.24 & -0.05 \\ 
  Hedges g: Random - Regression & -0.43 & -0.17 & -0.05 & 0.03 & 0.23 & -0.07 \\ 
  Log hazard ratio: Fixed - Copas & -0.02 & -0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
  Log hazard ratio: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.03 & 0.01 \\ 
  Log hazard ratio: Fixed - Regression & -0.15 & -0.01 & 0.07 & 0.14 & 0.21 & 0.06 \\ 
  Log hazard ratio: Random - Regression & -0.15 & -0.03 & 0.07 & 0.15 & 0.23 & 0.06 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects. The row names indicate which outcome measure, meta-analysis and adjustment method is used} 
\label{adjustment.difference}
\end{table}

>>>>

\usepackage{alltt}
\input{header.sty}   % packages, layout and standard macros
\input{newCommands.tex}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jun 28 14:09:15 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lllrrrr}
  \hline
Study & Comparison & Outcome & Events & Total & Events\_c & Total\_c \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up & 11 & 41 & 11 & 41 \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up & 14 & 27 & 13 & 26 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Example of two results as given in the dataset. Events denotes the count of events in the treatment group while Events c the count of events in the group compared to. Further descriptive variables have been ommitted} 
\label{barbiturate.row}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jun 28 14:09:15 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Study & Comparison & Outcome \\ 
  \hline
Bohn 1989 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Bohn 1989 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Uncontrolled ICP during treatment \\ 
  Eisenberg 1988 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Death or severe disability at the end of follow-up (6 months) \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Uncontrolled ICP during treatment \\ 
  Perez-Barcena 2008 & Pentobarbital vs Thiopental & Hypotension during treatment \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Death at the end of follow-up (1 year) \\ 
  Schwartz 1984 & Barbiturate vs Mannitol & Uncontrolled ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Death or severe disability at the end of follow-up \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean ICP during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean arterial pressure during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Hypotension during treatment \\ 
  Ward 1985 & Barbiturate vs no barbiturate & Mean body temperature during treatment \\ 
   \hline
\end{tabular}
\endgroup
\caption{Barbiturate and head injury review. In the columns, study names, comparison and outcome measure of the results are given} 
\label{barbiturates}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jun 28 14:09:15 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lr}
  \hline
  \hline
Missing mean values and mean differences & 984 \\ 
  Missing standard deviations and standard errors & 1300 \\ 
  Missing sample sizes & 12173 \\ 
  Missing study year & 44649 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Number of missing variables and measurements in the dataset} 
\label{missing}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jun 28 14:09:15 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
Outcome measure & n & Percentage \\ 
  \hline
Risk Ratio & 232583 & 50.1\% \\ 
  Mean Difference & 102315 & 22.1\% \\ 
  Odds Ratio & 49372 & 10.6\% \\ 
  Std. Mean Difference & 40535 & 8.7\% \\ 
  Peto Odds Ratio & 19122 & 4.1\% \\ 
  Hazard Ratio & 6566 & 1.4\% \\ 
  Risk Difference & 6234 & 1.3\% \\ 
  Rate Ratio & 2283 & 0.5\% \\ 
  other & 4810 & 1\% \\ 
   \hline
\end{tabular}
\endgroup
\caption{Frequencies of outcome measures among results. n denotes the total number 
             of results with the outcome measure and percentage the percentage of the outcome measure,} 
\label{outcome.measure.frequencies}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jun 28 14:09:15 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lll}
  \hline
n & Number of groups & Cumulative sum of groups \\ 
  \hline
1 & 102344 & 186300 \\ 
  2 & 31686 & 83956 \\ 
  3 & 16072 & 52270 \\ 
  4 & 9628 & 36198 \\ 
  5 & 6444 & 26570 \\ 
  6 & 4230 & 20126 \\ 
  7 & 2961 & 15896 \\ 
  8 & 2114 & 12935 \\ 
  9 & 1592 & 10821 \\ 
  10 & 1238 & 9229 \\ 
  11 & 921 & 7991 \\ 
  12 & 702 & 7070 \\ 
  13 & 585 & 6368 \\ 
  14 & 455 & 5783 \\ 
  15 & 5328 & 5328 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Cumulative number of groups with number of reproduction trials >= n} 
\label{repr.groups}
\end{table}

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jun 28 16:35:30 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{ccc}
  \hline
Count & Binary Outcomes & Continuous and Survival \\ 
  \hline
  0 & 65.9 \% & 68.4 \% \\ 
    1 & 16.4 \% & 9.6 \% \\ 
    2 & 8.6 \% & 9.1 \% \\ 
    3 & 5.6 \% & 10.6 \% \\ 
    4 & 2.9 \% & 2.3 \% \\ 
    5 & 0.6 \% & NA \% \\ 
   \hline
\end{tabular}
\endgroup
\caption{Counts Number of significant test results per meta-analysis, separated
       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
       applied} 
\label{number.sig.tests}
\end{table}

When only looking at small study effect tests, 29.1\% of binary outcome tests and 26.5\% of survival and continuous outcome tests had at least one significant result. After applying the bonferroni correction for multiple testing, this shrinks to 10.9\& for binary and 12.1\% for continuous and survival outcomes. \\
When comparing significant findings for small study effect tests and excess significance tests, we will only do so with Harbord's or Egger's test. 22.4\% of binary outcome analyses had at least one of the two test $p$-values being significant, and equivalently, 28\% for continuous and survival outcomes. Again, the numbers change to 13.3\% for binary outcomes and 17.2\% for continuous and survival outcomes after applying the bonferroni correction. \\
3\% have significant Harbord's test result and significant excesss significance test result  (1.1\% with bonferroni). Of the continuous outcomes, we have 6.1\% with Egger's test and 1.8\% with Bonferroni correction.

@@

There are two possibilities when adjusting the pooled treatment effect of meta-analyses for publication bias. The absolute size of the treatment effect can be smaller, or larger after adjustment. Additionally, it is of interest by how much the treatment effect is diminishued or increased. \\
Figure \ref{fig:adjustment.size} displays the difference between the meta-analysis pooled treatment effect $\theta_M$ and the adjusted treatment effect $\theta_\textrm{Adj.}$ for the copas and regression adjustment methods and fixed and random effects meta-analysis. The treatment effects are mirrored on the positive side, such that a positive difference indicates that the effect size was smaller after adjustment (and analogously, larger if the difference is negative). For better illustration, some very large and very small differences have been ommitted in the $z$-score and Hedges $g$ histogramms; the missing differences are provided in Table \ref{missing.differences}. Additionally to the histogramms, Table \ref{adjustment.difference} shows the quantiles and means for the various differences.\\
Copas estimates are equal to random effect in 1331 for $z$-score based analysis, 1144 for Hedges $g$ based analysis (and 1056 for analysis based on original effect measures). \\
We see in Figure \ref{fig:adjustment.size} that bot reduction and amplification of original effect size occurs frequently. Nevertheless, there are more adjustments towards smaller effects for $z$-scores and Hedges $g$, regardless of the reference meta-analysis method. Survival outcomes, and $z$-scores meta-analyses and copas adjustment differences are exception to this. The larger proportion of reduction is mostly also reflected in the means and medians in Table \ref{adjustment.difference}. They are mostly around zero or larger, although not to a large extent. There is more extensive downward correction of effect sizes if random effects meta-analysis is used as the reference.

@@

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jun 28 16:35:32 2019
\begin{table}[ht]
\centering
\begingroup\tiny
\begin{tabular}{lcccrrrrrrrr}
  \hline
meta.id & file.nr & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
  \hline
2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.43 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
  18658 & 18658 & 2 & 0 & 1.16 & 1.14 & 1.16 & 1.17 & 1.40 & 2.85 & 1.40 & 1.74 \\ 
  46472 & 46472 & 1 & 1 & 1.79 & 1.44 & 1.79 & 0.66 & 0.12 & 6.97 & 6.97 & 0.79 \\ 
  52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
  60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.58 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
  73769 & 73769 & 3 & 1 & -0.14 & 0.00 & 214760.42 & -0.04 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
  79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
  90138 & 90138 & 3 & 0 & 0.31 & 0.80 & 0.31 & 0.55 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
  97356 & 97356 & 2 & 0 & -0.08 & -0.33 & -0.08 & -0.17 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
  98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.91 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 71.80 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
  119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.11 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 498188.34 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects
             of Figure 
ef{fig:adjustment.size}. Abbreviations are used for z-score (z) and Hedges g (g)} 
\label{missing.differences}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jun 28 16:35:32 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lcccccc}
  \hline
 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
  \hline
z-score: Fixed - Copas & -0.05 & -0.01 & -0.00 & 0.01 & 0.05 & -402.37 \\ 
  z-score: Random - Copas & -0.01 & 0.00 & 0.00 & 0.00 & 0.04 & -159.98 \\ 
  z-score: Fixed - Regression & -0.13 & -0.04 & 0.01 & 0.05 & 0.15 & 0.01 \\ 
  z-score: Random - Regression & -0.16 & -0.03 & 0.02 & 0.07 & 0.18 & 0.02 \\ 
  Hedges g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.09 & 0.02 \\ 
  Hedges g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.14 & 0.04 \\ 
  Hedges g: Fixed - Regression & -0.24 & -0.04 & 0.04 & 0.13 & 0.39 & 0.05 \\ 
  Hedges g: Random - Regression & -0.23 & -0.03 & 0.05 & 0.17 & 0.43 & 0.07 \\ 
  Log hazard ratio: Fixed - Copas & -0.03 & 0.00 & 0.00 & 0.00 & 0.02 & -0.01 \\ 
  Log hazard ratio: Random - Copas & -0.03 & 0.00 & 0.00 & 0.00 & 0.00 & -0.01 \\ 
  Log hazard ratio: Fixed - Regression & -0.21 & -0.14 & -0.07 & 0.01 & 0.15 & -0.06 \\ 
  Log hazard ratio: Random - Regression & -0.23 & -0.15 & -0.07 & 0.03 & 0.15 & -0.06 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects. The row names indicate which outcome measure, meta-analysis and adjustment method is used} 
\label{adjustment.difference}
\end{table}
